### 2024-06-03 acronyms/acronyms.tex
kwh
ocm
dot
mrs
eis
head fix
nepa
mca
cce
ic3

>>>>

\newacronym{kwh}{kWh}{Kilowatt-Hour}
\newacronym{eis}{EIS}{Environmental Impact Statement}
\newacronym{ocm}{OCRWM}{Office of Civilian Radioactive Waste Management}
\newacronym{dot}{DOT}{Department of Transportation}
\newacronym{mrs}{MRS}{Monitored Retrievable Storage}
\newacronym{nep}{NEPA}{National Environmental Policy Act}
\newacronym{mca}{MC\&A}{Materials Control and Accountability}
\newacronym{rv}{R\&V}{Reproducibility \& Validation}
\newacronym{cce}{CCE}{Consequence-Driven Cyber-informed Engineering}
\newacronym{ic3}{IC3I}{Intermountain Center for the Cybersecurity of Critical Infrastructure}
